Top-Down Graph-Based Neuron Reconstruction

### 2017-11-14 papers/cvpr2018/2_method.tex
paper: cleaned up wording

\subsection{Edge Weights Assignment}
We aim to assign non-negative edge weights $w_e$, where adjacent nodes (endpoints $e$ in $\mathbb{S}_c$) connected with a big edge weight has higher chance to be merged to the same segment.
Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
%Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}

>>>>

\subsection{Edge Weights Assignment}
We assign non-negative edge weights $w_e$ to each edge where the weight corresponds to the probability two nodes belong to the same neuron.
Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
%Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}

### 2017-11-14 papers/cvpr2018/3_evaluation.tex
paper: cleaned up wording

We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing} (VI-s). Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively. Since we are measuring the entropy between two clusterings, better VI-s scores are closer to the origin.
In Fig.~\ref{fig:variation-of-information}, we compute VI-s scores for the input over-segmentation result at different stopping thresholds of agglomeration.

>>>>

We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing} (VI-s). Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively. Since we are measuring the entropy between two clusterings, better VI scores are closer to the origin.
In Fig.~\ref{fig:variation-of-information}, we compute VI scores for the input over-segmentation at different stopping thresholds of agglomeration.
